Decomposing labelled proof theory for intuitionistic modal logic

### 2019-08-31 caleidoscope/caleidoscope.tex
extensions section

\todo{The idea of this section is to show the things that our system could do (extensions of the logic) and Simpson could not.}

\todo{Scott-Lemmon with the new rules (general rules for F2, F1, etc) for the system and the lemma that shows that each rule is admissible}

>>>>

\marianela{The idea of this section is to show the things that our system could do (extensions of the logic) and Simpson could not.}
